A Possibilistic Valid-time Model

### 2011-12-13 trunk/ipmu2012/conclusions.tex
Normally, only details left

We presented a valid-time model to represent and querying ill-known temporal intervals. The main advantage of the framework is that it is always possible to get both a possibility and a necessity measures for every comparison, which is also useful for ranking purposes. The framework models the Allen's relations and it has the flexibility to model specific and more complex relations by means of ill-known constraints.  As future work, the time interval in the query specification would also be ill-known.

>>>>

We presented a Valid-time model to represent and query ill-known temporal intervals. The main advantage of this framework is that it is always possible to get both a possibility and a necessity measures for every comparison, which is also useful for ranking purposes. The framework models the Allen's relations and it has the flexibility to model specific and more complex relations by means of ill-known constraints.  As future work, the time interval in the query specification would also be ill-known.

### 2011-12-13 trunk/ipmu2012/proposal.tex
Normally, only details left

@@

FROM HERE

%\begin{example} 
\subsubsection{The database}
Consider a database describing car models, containing general attributes (model name, manufacturer, car segment) and one temporal attribute containing the approximate period of time during which the car model was sold. The temporal data is stored as explained in subsection \ref{subsec:storage}. The value for $D$ is stored in \emph{yyyy} format and $a$ and $b$ are represented by an integer, for the convenience of the representation. Therefore the chronons in our example will be years. The ID field identifies a car model while the field Instance ID (IID) identifies the instance for a car model.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Sample table for the car models. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht]
\centering
\begin{tabular}{c c c c c c c}
\hline
ID & IID & Segment & Manufacturer & Name & Start & End  \\ [0.5ex]
\hline
001 & 1 & B & Peugeot & 205 & [1985,2,3] & [1997,2,1] \\
002 & 1 & C & Peugeot & 305 & [1977,2,2] & [1989,2,3] \\
003 & 1 & B & Citroen & C2 & [2002,2,2] & [2006,1,1] \\
001 & 2 & B & Peugeot & 206 & [2000,1,2] & [2011,2,1] \\
001 & 3 & B & Peugeot & 207 & [2006,1,1] & [2011,1,1]\\
\hline
\end{tabular}
\vspace{10pt}
\caption{Sample database}
\label{tb:car-models}
\end{table}

\textbf{The query}
Consider the following query:

\emph{The user wants to obtain a list of models in the segment B for the manufacturer Peugeot before the year interval 2001-2005.}

The query is translated to the following expression, using equation \eqref{eq:query-definition}. The evaluation for the criteria are presented in the result table \ref{tb:results}.

\begin{center}
$\tilde{Q} = \left(  c^{time}, c_{segment} \right)$
\end{center}

Where:
\begin{itemize}
\item
$c^{time}\ = \ ( \left[ 2001,\ 2005 \right],\ $  before $)$.
\item
$c_{segment}\ = \ $ Peugeot.
\end{itemize}

\begin{table}[ht]
\caption{Result table and ranking}
\centering
\begin{tabular}{c c c c c c c}
\hline
ID & IID &  $\Pos_{c^{time}}$ &$\Nec_{c^{time}}$ & $e(C^{time})$ & $c_{segment}$ & rank ($\omega=0.5$) \\ [0.5ex]
\hline
001 & 1 & 1 &  1 & 1 & 1 & 1 \\
002 & 1 & 1 & 1 & 1 & 0.5 & 0.75 \\
003 & 1 & 1 & 0.5 & 0.75 &0 & 0.375\\
001 & 2 & 1 & 0 & 0.5 &1 & 0.75 \\
001 & 3 & 0 & 0 & 0 &1 & 0.5\\
\hline
\end{tabular}
\label{tb:results}
\end{table}
%\end{example}

>>>>

\vspace{-5pt}

@@

%\begin{example} 
\subsubsection{The database}
Consider example database \ref{tb:car-models} describing car models, containing general attributes (model name, manufacturer, car segment) and one temporal attribute containing the approximate period of time during which the car model was sold. The temporal data is stored as explained in subsection \ref{subsec:storage}. Let the chronons in our example be years. The value for $D$ is stored in \emph{yyyy} format and $a$ and $b$ are represented by an integer. The ID field identifies a car model while the field Instance ID (IID) identifies the instance for a car model, thus a car model in a certain state.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Sample table for the car models. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
\centering
\begin{tabular}{c c c c c c c}
\hline
ID & IID & Segment & Manufacturer & Name & Start & End  \\ [0.5ex]
\hline
001 & 1 & B & Peugeot & 205 & [1985,2,3] & [1997,2,1] \\
002 & 1 & C & Peugeot & 305 & [1977,2,2] & [1989,2,3] \\
003 & 1 & B & Citroen & C2 & [2002,2,2] & [2006,1,1] \\
001 & 2 & B & Peugeot & 206 & [2000,1,2] & [2011,2,1] \\
001 & 3 & B & Peugeot & 207 & [2006,1,1] & [2011,1,1]\\
\hline
\end{tabular}
\vspace{10pt}
\caption{Example database}
\label{tb:car-models}

\vspace{-30pt}

\subsubsection{The query}
Consider the following query:

\begin{center}
\emph{The user wants to obtain a list of models from segment B, made by manufacturer Peugeot before the year interval 2001-2005}
\end{center}

Using the introduced notations, the query is translated to the following expression:

\vspace{-10pt}

\begin{center}
$\tilde{Q} = \left(Q^{time}, Q\right)$
\end{center}

\vspace{-10pt}

In this expression:
%\begin{itemize}
%\item
%$Q^{time}\ = \ ( \left[ 2001,\ 2005 \right],\ $  before $)$.
%\item
%$c_{segment}\ = \ $ Peugeot.
%\end{itemize}

\vspace{-15pt}

\begin{align}
Q^{time} & = \left(\left[ 2001, 2005 \right], before\right) \\
Q & = \left(Segment =  B\right) \wedge \left(Manufacturer = Peugeot\right)
\end{align}

The evaluation for the criteria are presented in the result table \ref{tb:results}.

\begin{table}[ht]
\caption{Result table and ranking}
\centering
\begin{tabular}{c c c c c c c}
\hline
ID & IID &  $\Pos_{Q^{time}}$ & $\Nec_{Q^{time}}$ & $e_{Q^{time}} (rescaled)$ & $Q$ & $e_{final}$ ($\omega=0.5$) \\ [0.5ex]
\hline
001 & 1 & 1 &  1 & 1 & 1 & 1 \\
002 & 1 & 1 & 1 & 1 & 0.5 & 0.75 \\
003 & 1 & 1 & 0.5 & 0.75 &0 & 0.375\\
001 & 2 & 1 & 0 & 0.5 &1 & 0.75 \\
001 & 3 & 0 & 0 & 0 &1 & 0.5\\
\hline
\end{tabular}
\label{tb:results}
\end{table}
%\end{example}
